Towards open collaboration in biomedical and health research: A scoping review

### 2022-09-05 doc/protocol.Rmd
Review protocol

---
title: "Towards open collaboration in biomedical and health research: A scoping review"
shorttitle: "Scoping review of open collaboration"
date: "`r Sys.setlocale('LC_TIME', 'C'); format(Sys.time(), '%d\\\\. %B %Y')`"
author: 
  - name: Luke W. Johnston
    affiliation: 1
  - name: Daniel Ibsen
    affiliation: 1
  - name: Hannah Chatwin
    affiliation: 1
  - name: Mario Garcia
    affiliation: 1
affiliation:
  - id: 1
    institution: Steno Diabetes Center Aarhus, Denmark
  - id: 2
    institution: 
output: prereg::prereg_pdf
---

@@

Since scientific research now almost always requires working with other
people. With the increasing emphasis on and demand for science to be
more open, how we collaborate together is a key component to making
science more easily open from the start of any project. But how do we
collaborate in an open and transparent way? What are the best practices
and tools we can use? What is an ideal collaborative workflow and how
close or far are we from this ideal in reality? This project aims to
address some of these questions.

@@

Scoping review on the literature around open collaboration.

@@

    -   5 years in the past, until approximately 2017-01-01, to capture
        current/most recent practices.

@@

We aim to identify at least 1000 articles in the initial first
literature extraction.

@@

In terms of database searches, we aim to limit the search until the end
date (maximum 2022-11-31). Searches will be concluded when we reach
conceptual saturation (i.e., when it is determined that we are not
identifying any new concepts/resources). Depending on the quantity of
records retrieved, even after further filtering, we may randomly select
a large enough sample that each person can go through and manually
review them. In the interests of feasibility, a maximum for 4 books will
be selected and evaluated. Books will be selected based on a consensus
in the research group.

@@

The primary "variables" of interest will be the article title, abstract,
topic list, and full length article. In addition to these variables, we
will also obtain article metadata, such as publication date, URL/DOI,
and author list.

>>>>

---
title: "Towards open collaboration in biomedical and health research: A scoping review"
shorttitle: "Scoping review of open collaboration"
date: "`r Sys.setlocale('LC_TIME', 'C'); format(Sys.time(), '%d\\\\. %B %Y')`"
author: 
  - name: Luke W. Johnston
    affiliation: "1,2"
  - name: Daniel Ibsen
    affiliation: 1
  - name: Hannah Chatwin
    affiliation: 2
  - name: Mario Garcia
    affiliation: 3
affiliation:
  - id: 1
    institution: Steno Diabetes Center Aarhus, Denmark
  - id: 2
    institution: Aarhus University, Denmark
   - id: 3
    institution: Copenhagen University, Denmark
output: prereg::prereg_pdf
---

@@

Scientific research now almost always requires working with other
people. With the increasing emphasis on and demand for science to be
more open, how we collaborate together is a key component to making
science more open from the start of any project. But how do we
collaborate in an open and transparent way? What are the best practices
and tools we can use? What is an ideal collaborative workflow and how
close or far are we from this ideal in reality? This project aims to
address some of these questions.

@@

Scoping review on literature relating to open collaboration.

@@

    -   Documents published >5 years in the past (defined as before 2017-01-01) to capture
        current/most recent practices.

@@

We aim to identify at least 1000 articles in the initial database search.

@@

In terms of database searches, we aim to limit the search until the end
date (maximum 2022-11-31). Searches will be concluded when we reach
conceptual saturation (i.e., when it is determined that we are not
identifying any new concepts/resources). Depending on the quantity of
records retrieved, even after further filtering, we may randomly select
a sample that each person can go through and manually
review them. In the interests of feasibility, a maximum for 4 books will
be selected and evaluated. Books will be selected based on consensus
in the research group.

@@

The primary "variables" of interest will be the article title, abstract,
topic list, and full length article including content relating to open collaboration. In addition to these variables, we
will also obtain article metadata, such as publication date, URL/DOI,
and author list.
